Sparse Function-space Representation \\ of Neural Networks

### 2023-05-13 paper/main.tex
bibs to related work

%Current state of affairs 
Recent work on techniques (\eg, \cite{list}) for converting trained neural networks from weight space to function space allow a principled mathematical approach for analyzing the behaviour \cite{add}, performing probabilistic inference \cite{add}, and quantifying uncertainty in neural networks \cite{add}. The methods rely on linearizing the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (kernel)---defining a Gaussian process (GP, \cite{rasmussen2006}). GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they are a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}. 
%Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations. In such scenarios such as in many reinforcement learning environments neural networks are used as the surrogate model. However, uncertainty is still essential to ensure effective exploration for sequential algorithms. Successful approaches have attempted to blend neural networks with uncertainty estimates around predictions, allowing for sophisticated exploration strategies. However, there has been limited use of hybrid models that possess the feature representation ability of neural networks but also attractive the properties of GPs, such a hybrid method we propose in this paper.

@@

\subsection{Related work}
\label{sec:related}
%
% Introduce the laplace GGN + shortcomings
One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxbergerLaplace2021}, which takes a trained neural network and linearises it around the optimal weights. The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immerScalable2021}, and is linear with respect to the weights. Therefore, as shown in \citep{immerScalable2021, khan2019approximate}, the linear model can be converted to a Gaussian process (GP), which is then used to obtain the uncertainty estimates.
However, the GP introduces a computational scaling that is cubic in the number of data points ($\mathcal{O}(n^3)$). Many approaches apply crude approximations to alleviate the computational costs, \eg, considering only a subset of the training datas, but are still obtain good uncertainty estimates \citep{immerScalable2021}\todo{other methods?}.

>>>>

%Current state of affairs 
Recent work on techniques (\eg, \cite{list}) for converting trained neural networks from weight space to function space allow a principled mathematical approach for analyzing the behaviour \cite{add}, performing probabilistic inference \cite{add}, and quantifying uncertainty in neural networks \cite{add}. The methods rely on linearizing the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}). GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they are a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}. 
%Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations. In such scenarios such as in many reinforcement learning environments neural networks are used as the surrogate model. However, uncertainty is still essential to ensure effective exploration for sequential algorithms. Successful approaches have attempted to blend neural networks with uncertainty estimates around predictions, allowing for sophisticated exploration strategies. However, there has been limited use of hybrid models that possess the feature representation ability of neural networks but also attractive the properties of GPs, such a hybrid method we propose in this paper.

@@

\subsection{Related work}
\label{sec:related}
%
% General Bayesian deep learning
Bayesian deep learning~\cite{Wilson:ensembles,neal1995bayesian} has recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021marginal,antoran2022marginal}) with advancements in prior specification (\eg, \cite{meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \cite{blei2017variational}, deep ensembles \cite{lakshminarayanan2017simple}, MC dropout \cite{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each having strengths and weaknesses. % point out strngths and weaknesses for each

% Introduce the laplace GGN + shortcomings
One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxberger2021laplace}, which takes a trained neural network and linearises it around the optimal weights. The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immerScalable2021}, and is linear with respect to the weights. Therefore, as shown in \citep{immerScalable2021, khan2019approximate}, the linear model can be converted to a Gaussian process (GP), which is then used to obtain the uncertainty estimates.
However, the GP introduces a computational scaling that is cubic in the number of data points ($\mathcal{O}(n^3)$). Many approaches apply crude approximations to alleviate the computational costs, \eg, considering only a subset of the training datas, but are still obtain good uncertainty estimates \citep{immerScalable2021}\todo{other methods?}.

The Hessian can be efficiently approximated using the generalised Gauss-Newton algorithm \cite{botev2017practical} or by Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac}.
